Automated Synthesis of State-Space Digital Systems

### 2016-12-21 cav2017/cav2017.tex

The first plant represents a DC motor position model from~\cite{CTMS}. It is a third order system and presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
$$
\textbf{A}=\left[\begin{array}{ccc}
0		& 1 		& 0						\\
0 		& -1.087	& 8587					\\
0		& -9964		& -1.455\times 10^{6}	\\
\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
0 \\ 0 \\ -1.455\times10^{6}
\end{array}\right]
$$
%
$$
\textbf{C}=\left[\begin{array}{ccc}
1 & 0 & 0\\
\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
\theta \\ \dot{\theta} \\ i \\
\end{array}\right],
$$
where the states $\theta$, $\dot{\theta}$, and $i$ are respectively the rotor angular position, rotor angular rate and the current of armature. The DC motor is stable in open loop.

The second benchmark is an aircraft pitch dynamics model extracted from~\cite{CTMS}. It is a third order system and it presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
$$
\textbf{A}=\left[\begin{array}{ccc}
-0.313	& 56.7 		& 0		\\
-0.0139	& -0.426	& 0		\\
0		& 56.7		& 0		\\
\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
0.232 \\ 0.0203 \\ 0
\end{array}\right]
$$
%
$$
\textbf{C}=\left[\begin{array}{ccc}
0 & 0 & 1\\
\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
\alpha \\ \dot{\theta} \\ \theta \\
\end{array}\right],
$$
where the states $\alpha$, $\dot{\theta}$, and $\theta$ are respectively the aircraft attack angle, pitch rate and the pitch angle. The aircraft pitch dynamic is critically stable in open loop, with a pole in origin of $s$-plane.

The third benchmark is a ball magnetic levitation model extracted from~\cite{maglev}. It is a third order system presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
$$
\textbf{A}=\left[\begin{array}{ccc}
0		& 1 		& 0		\\
1752	& 0			& -34.07\\
0		& 0			& -38.27\\
\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
0 \\ 0 \\ 1.923
\end{array}\right]
$$
%
$$
\textbf{C}=\left[\begin{array}{ccc}
1 & 0 & 0\\
\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
z \\ \dot{z} \\ i \\
\end{array}\right],
$$
where the states $z$, $\dot{z}$, and $i$ are respectively the vertical displacement of the ball, its rate and the coil current. This system  is unstable in open loop.

There are three benchmarks representing classic DC-DC converters: buck, boost, and buck-boost. They are SISO second-order systems stable in open-loop, and their state vector is $\textbf{x}=\textbf{x}=\left[\begin{array}{c}
i_{L} \\ v_{C}\\
\end{array}\right]$, where $i_{L}$ is the current in the coil and $v_{c}$ is the voltage on the capacitor. The matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, and $\textbf{D}$ for the buck converter are:
$$
\textbf{A}=\left[\begin{array}{cc}
0		& -500 \\
4545	& -1515\\
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
125 \\ 0 \\
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
0 & 1\\
\end{array}\right],~ \textbf{D}= 0.
$$

The matrices of the boost converter are:
$$
\textbf{A}=\left[\begin{array}{cc}
0		& -375 \\
3409	& -1515\\
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
500 \\ 0 \\
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
0 & 1\\
\end{array}\right],~ \textbf{D}= 0.
$$

Finally, the matrices of the buck-boost converter are:
$$
\textbf{A}=\left[\begin{array}{cc}
0		& 375 \\
-3409	& -1515\\
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
125 \\ 0 \\
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
0 & 1\\
\end{array}\right],~ \textbf{D}= 0.
$$

Additionally, various dynamic systems model were extracted from~\cite{Franklin15} and incorporated to our test suite. They are: 
\begin{itemize}
\item{\textbf{automotive cruise control system:} 
$$
\textbf{A}=-0.05,~ \textbf{B} = 0.03125~
\textbf{C}=0.032,~ \textbf{D}= 0;
$$
}
\item{\textbf{DC motor:} 
$$
\textbf{A}=\left[\begin{array}{cc}
-1000		& -13 \\
-8			& 0\\
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
4 \\ 0 \\
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
0 & 6.25\\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{helicopter longitudinal motion:} 
$$
\textbf{A}=\left[\begin{array}{ccc}
-0.42		& 0.0168		& -0.396	\\
0.5			& 0				& 0			\\
0			& 0.5 			& 0			
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
16 \\ 0 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{ccc}
0.6125	& -0.6125	& 15.44 \\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{inverted pendulum cart position:} 
$$
\textbf{A}=\left[\begin{array}{cccc}
0		& 1		& 0 	& 0	\\
1		& 0		& 0		& 0	\\
0		& 1 	& 0		& 0 \\
0		& 0		& 1 	& 0 \\	
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
1 \\ 0 \\ 0 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cccc}
0	& 0	& 1 & -0.75 \\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{inverted pendulum angle:} 
$$
\textbf{A}=\left[\begin{array}{cc}
0		& 1	\\
1		& 0	\\
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
1 \\ 0 \\ 0 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
 0	& 1 \\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{magnetic pointer:} 
$$
\textbf{A}=\left[\begin{array}{ccc}
-0.271		& -0.05336	& 0	\\
0.03125		& 0			& 0	\\
0			& 0.01562 	& 0	\\	
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
1 \\ 0 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{ccc}
0	& -0.5888	& -0.2562 \\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{magnetic suspension:} 
$$
\textbf{A}=\left[\begin{array}{cc}
0		& 31.25	\\
32		& 0		\\	
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
8 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
0	& 9.766 	\\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{pendulum:} 
$$
\textbf{A}=\left[\begin{array}{cc}
0		& -2.453	\\
4		& 0			\\	
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
4 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
-1.225	& -2.15 	\\
\end{array}\right],~ \textbf{D}= 9.8;
$$
}
\item{\textbf{1/4 car suspension:} 
$$
\textbf{A}=\left[\begin{array}{cccc}
-516.1	& -222.1& -79.75& -33.06	\\
256		& 0		& 0		& 0			\\
0		& 64 	& 0		& 0 \\
0		& 0		& 32 	& 0 \\	
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
8 \\ 0 \\ 0 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cccc}
0	& 0	& 9.969 & 4.133 \\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{computer tape driver:} 
$$
\textbf{A}=\left[\begin{array}{ccc}
-1760		& -976.6	& -457.8	\\
1024		& 0			& 0			\\
0			& 512 		& 0			\\	
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
8 \\ 0 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{ccc}
1.5	& 2.051	& 1.144 \\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{USCG cutter Tampa heading angle:} 
$$
\textbf{A}=\left[\begin{array}{ccc}
-0.271		& -0.05336	& 0	\\
0.03125		& 0			& 0			\\
0			& 0.01562 	& 0			\\	
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
1 \\ 0 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{ccc}
0	& -0.5888	& -0.2562 \\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\end{itemize}

\begin{table}[]

@@

\label{State-space benchmarks}

>>>>

The table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from literature~\cite{Franklin15,converters,maglev,CTMS} and adopted in our experiments.

%The first plant represents a DC motor position model from~\cite{CTMS}. It is a third order system and presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
%$$
%\textbf{A}=\left[\begin{array}{ccc}
%0		& 1 		& 0						\\
%0 		& -1.087	& 8587					\\
%0		& -9964		& -1.455\times 10^{6}	\\
%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
%0 \\ 0 \\ -1.455\times10^{6}
%\end{array}\right]
%$$
%%
%$$
%\textbf{C}=\left[\begin{array}{ccc}
%1 & 0 & 0\\
%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
%\theta \\ \dot{\theta} \\ i \\
%\end{array}\right],
%$$
%where the states $\theta$, $\dot{\theta}$, and $i$ are respectively the rotor angular position, rotor angular rate and the current of armature. The DC motor is stable in open loop.
%
%The second benchmark is an aircraft pitch dynamics model extracted from~\cite{CTMS}. It is a third order system and it presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
%$$
%\textbf{A}=\left[\begin{array}{ccc}
%-0.313	& 56.7 		& 0		\\
%-0.0139	& -0.426	& 0		\\
%0		& 56.7		& 0		\\
%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
%0.232 \\ 0.0203 \\ 0
%\end{array}\right]
%$$
%%
%$$
%\textbf{C}=\left[\begin{array}{ccc}
%0 & 0 & 1\\
%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
%\alpha \\ \dot{\theta} \\ \theta \\
%\end{array}\right],
%$$
%where the states $\alpha$, $\dot{\theta}$, and $\theta$ are respectively the aircraft attack angle, pitch rate and the pitch angle. The aircraft pitch dynamic is critically stable in open loop, with a pole in origin of $s$-plane.
%
%The third benchmark is a ball magnetic levitation model extracted from~\cite{maglev}. It is a third order system presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
%$$
%\textbf{A}=\left[\begin{array}{ccc}
%0		& 1 		& 0		\\
%1752	& 0			& -34.07\\
%0		& 0			& -38.27\\
%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
%0 \\ 0 \\ 1.923
%\end{array}\right]
%$$
%%
%$$
%\textbf{C}=\left[\begin{array}{ccc}
%1 & 0 & 0\\
%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
%z \\ \dot{z} \\ i \\
%\end{array}\right],
%$$
%where the states $z$, $\dot{z}$, and $i$ are respectively the vertical displacement of the ball, its rate and the coil current. This system  is unstable in open loop.
%
%There are three benchmarks representing classic DC-DC converters: buck, boost, and buck-boost. They are SISO second-order systems stable in open-loop, and their state vector is $\textbf{x}=\textbf{x}=\left[\begin{array}{c}
%i_{L} \\ v_{C}\\
%\end{array}\right]$, where $i_{L}$ is the current in the coil and $v_{c}$ is the voltage on the capacitor. The matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, and $\textbf{D}$ for the buck converter are:
%$$
%\textbf{A}=\left[\begin{array}{cc}
%0		& -500 \\
%4545	& -1515\\
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%125 \\ 0 \\
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cc}
%0 & 1\\
%\end{array}\right],~ \textbf{D}= 0.
%$$
%
%The matrices of the boost converter are:
%$$
%\textbf{A}=\left[\begin{array}{cc}
%0		& -375 \\
%3409	& -1515\\
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%500 \\ 0 \\
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cc}
%0 & 1\\
%\end{array}\right],~ \textbf{D}= 0.
%$$
%
%Finally, the matrices of the buck-boost converter are:
%$$
%\textbf{A}=\left[\begin{array}{cc}
%0		& 375 \\
%-3409	& -1515\\
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%125 \\ 0 \\
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cc}
%0 & 1\\
%\end{array}\right],~ \textbf{D}= 0.
%$$
%
%Additionally, various dynamic systems model were extracted from~\cite{Franklin15} and incorporated to our test suite. They are: 
%\begin{itemize}
%\item{\textbf{automotive cruise control system:} 
%$$
%\textbf{A}=-0.05,~ \textbf{B} = 0.03125~
%\textbf{C}=0.032,~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{DC motor:} 
%$$
%\textbf{A}=\left[\begin{array}{cc}
%-1000		& -13 \\
%-8			& 0\\
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%4 \\ 0 \\
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cc}
%0 & 6.25\\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{helicopter longitudinal motion:} 
%$$
%\textbf{A}=\left[\begin{array}{ccc}
%-0.42		& 0.0168		& -0.396	\\
%0.5			& 0				& 0			\\
%0			& 0.5 			& 0			
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%16 \\ 0 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{ccc}
%0.6125	& -0.6125	& 15.44 \\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{inverted pendulum cart position:} 
%$$
%\textbf{A}=\left[\begin{array}{cccc}
%0		& 1		& 0 	& 0	\\
%1		& 0		& 0		& 0	\\
%0		& 1 	& 0		& 0 \\
%0		& 0		& 1 	& 0 \\	
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%1 \\ 0 \\ 0 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cccc}
%0	& 0	& 1 & -0.75 \\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{inverted pendulum angle:} 
%$$
%\textbf{A}=\left[\begin{array}{cc}
%0		& 1	\\
%1		& 0	\\
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%1 \\ 0 \\ 0 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cc}
% 0	& 1 \\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{magnetic pointer:} 
%$$
%\textbf{A}=\left[\begin{array}{ccc}
%-0.271		& -0.05336	& 0	\\
%0.03125		& 0			& 0	\\
%0			& 0.01562 	& 0	\\	
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%1 \\ 0 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{ccc}
%0	& -0.5888	& -0.2562 \\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{magnetic suspension:} 
%$$
%\textbf{A}=\left[\begin{array}{cc}
%0		& 31.25	\\
%32		& 0		\\	
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%8 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cc}
%0	& 9.766 	\\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{pendulum:} 
%$$
%\textbf{A}=\left[\begin{array}{cc}
%0		& -2.453	\\
%4		& 0			\\	
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%4 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cc}
%-1.225	& -2.15 	\\
%\end{array}\right],~ \textbf{D}= 9.8;
%$$
%}
%\item{\textbf{1/4 car suspension:} 
%$$
%\textbf{A}=\left[\begin{array}{cccc}
%-516.1	& -222.1& -79.75& -33.06	\\
%256		& 0		& 0		& 0			\\
%0		& 64 	& 0		& 0 \\
%0		& 0		& 32 	& 0 \\	
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%8 \\ 0 \\ 0 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cccc}
%0	& 0	& 9.969 & 4.133 \\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{computer tape driver:} 
%$$
%\textbf{A}=\left[\begin{array}{ccc}
%-1760		& -976.6	& -457.8	\\
%1024		& 0			& 0			\\
%0			& 512 		& 0			\\	
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%8 \\ 0 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{ccc}
%1.5	& 2.051	& 1.144 \\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{USCG cutter Tampa heading angle:} 
%$$
%\textbf{A}=\left[\begin{array}{ccc}
%-0.271		& -0.05336	& 0	\\
%0.03125		& 0			& 0			\\
%0			& 0.01562 	& 0			\\	
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%1 \\ 0 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{ccc}
%0	& -0.5888	& -0.2562 \\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\end{itemize}

\begin{table}[HTB]

@@

\label{table:State-space benchmarks}
